---
title: DANL Project
subtitle: "Data-Driven Mastery: Unlocking Business Potential"
author: 
  - Sophia Rodger 
  - Jake Marcell
  - Jake Knapp
  - Blaise Leone
  - Mac Bean 

toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

from: markdown+emoji
---

```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```

# Introduction

Welcome to the exploration of alcohol content trends in popular beer brands! In this project, we delve into a dataset containing information on different beer brands. Our focus is on understanding the variation in alcohol content among these brands, providing insights into the diverse world of beers. :beers: :clap:

# Data

The dataset beer_data contains a curated selection of beer brands. Let's begin by exploring the summary statistics to gain an initial understanding of the dataset. :beers:

## Summary Statistics

```{r}
beer_data <- read_csv('https://bcdanl.github.io/data/beer_markets.csv') 
```

```{r}
skim(beer_data) %>% 
  select(-n_missing)
```


## Alcohol Content in Beer Brands 

We aim to analyze the alcohol content of different beer brands. Let's visualize this with an insightful boxplot. :bar_chart: :beer:

```{r}

```
